---
title: "Daytracker additional data"
author: "Tamas Nagy"
date: "5/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(haven)
library(labelled)
library(here)
library(correlation)

```

# Data request

1.  The zero-order Pearson or Spearman correlation between physical activity (measured as a covariate) and the diurnal cortisol slope.
2.  The cortisol awakening response expressed as the raw mean difference of cortisol from awakening to peak (30 minutes later) and standard deviation in different levels of physical activity participation (high, low, no physical activity/sedentary, if data are available).

```{r}
# Read data
nf_raw <- read_sav(here("data/Hungary_scales.sav"))

variables <-
    tibble(nm = names(nf_raw),
           lab = var_label(nf_raw) %>% as.character())
```

## Variables
- Salivary cortisol was measured using salivettes.
- Cortisol was measured for a working day and a leisure day.
- Cortisol slope from waking through the day (excluding the waking + 30 sample) for work and leisure days. These slopes are computed from waking until 3:00pm. Values are change in nmol/l/min. These values are normally distributed so have not been logged.
- CAR was measured as the difference between waking+30min and waking cortisol.
- Exercise: A scale from 0: no/few exercise to 6: lots of exercise, the sum of moderate and vigorous exercise (both on a scale of 3: Three times or more a week 2: Once to twice a week 1: About once to three times a month 0: Never / hardly ever).


### 1. The zero-order Pearson or Spearman correlation between physical activity (measured as a covariate) and the diurnal cortisol slope.


```{r}
nf_raw %>% 
    select(`Exercise` = extot,
           `Cortisol slope (working day)` = cortwregsl1, 
           `Cortisol slope (Leisure day)` = cortlregsl1) %>% 
    correlation(method = "spearman", p_adjust = "none") %>% 
    knitr::kable(digits = 2)
```


### 2. The cortisol awakening response expressed as the raw mean difference of cortisol from awakening to peak (30 minutes later) and standard deviation in different levels of physical activity participation (high, low, no physical activity/sedentary, if data are available).

```{r}

nf_raw %>% 
    select(`Exercise` = extot,
           cortwcar, 
           cortlcar) %>% 
    group_by(Exercise) %>% 
    summarise(N = n(),
              `Mean CAR (working day)` = mean(cortwcar, na.rm = TRUE),
              `SD CAR (working day)` = sd(cortwcar, na.rm = TRUE),
              `Mean CAR (leisure)` = mean(cortlcar, na.rm = TRUE),
              `SD CAR (leisure)` = sd(cortlcar, na.rm = TRUE)) %>% 
    knitr::kable(digits = 2)
```

